Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-06-21 ms.tex
Add self-critical margin note
Add footnote about OpenMP

We evaluate the \ac{TOA}\nobreakdashes-only posterior at the centers of \ac{HEALPix} pixels at the lowest possible resolution. Then, we increase the resolution until 99.99\% of the \ac{TOA}\nobreakdashes-only posterior is contained within at least 3072 pixels. The numerically expensive \ac{SNR} integrals are done only for the pixels that comprise the 99.99th percentile at this resolution. All other pixels are set to zero.

@@

>>>>

\marginpar{Clumsy prose.}%
We evaluate the \ac{TOA}\nobreakdashes-only posterior at the centers of \ac{HEALPix} pixels at the lowest possible resolution. Then, we increase the resolution until 99.99\% of the \ac{TOA}\nobreakdashes-only posterior is contained within at least 3072 pixels. The numerically expensive \ac{SNR} integrals are done only for the pixels that comprise the 99.99th percentile at this resolution. All other pixels are set to zero.

@@

The \ac{SNR} marginalization integrals for different pixels may be evaluated in parallel. In our C language implementation, the loop over pixels is parallelized with OpenMP\footnote{http://openmp.org/}.
